Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-02 main.tex
Note

{\em Hyperproperties}, i.e. properties of pairs\leo{sets?} of
execution traces\footnote{\bcp{I'm not certain we're using the word
    correctly.  E.g., ``A hyperproperty is a set of properties [Clarkson and Schneider 2008, 2010]''}}, are the standard way of expressing security
properties\cn. In particular, {\em noninterference} is commonly
phrased as such a property: given two system states that seem
identical to an observer with low clearance, their execution traces
should also be indistinguishable\cn.

>>>>

{\em Hyperproperties}, i.e. properties of pairs\leo{sets?} of
execution traces\footnote{\bcp{I'm not certain we're using the word
    correctly.  E.g., ``A hyperproperty is a set of properties [Clarkson and
    Schneider 2008, 2010]''} \bcp{After more reading, I am still wondering
    if we're using the word the right way.  I think we mean something much
    less general---just a relation on traces.  So I think we should just say
    ``contoured relation'' (and maybe ``lockstep relation'').}}, are the
standard way of expressing security 
properties\cn. In particular, {\em noninterference} is commonly
phrased as such a property: given two system states that seem
identical to an observer with low clearance, their execution traces
should also be indistinguishable\cn.
